Demers Cartogram with Rivers

### 2023-07-14 paper/section/related.tex
draft: increase thumbnail size

{
\renewcommand{\arraystretch}{1.5}
\begin{table*}[!tb]
	\centering
	\resizebox{\textwidth}{!}{
		\begin{tabulary}{\textwidth}{|*{4}{l|}r|c|}
			\hhline{~|*{4}{-}|~}
			\multicolumn{1}{c|}{\textbf{Literature}} &
			\textbf{Title} &
			\textbf{Cartogram Type(s)} &
			\textbf{Geographic Region(s)} &
			\textbf{Number of Nodes} &
			\multicolumn{1}{c}{\textbf{Year}} \\
			\hline

			% \citet{auber2007Geographical} & \citep{auber2007Geographical} & US & 19 & 2007 \\
			% \hline
			\citet{warf2008Geography} & \citep{warf2008Geography} & Dorling & US & 3,142 & \citeyear{warf2008Geography} \\
			\hline
			\citet{sun2010Effectiveness} & \citep{sun2010Effectiveness} & Dorling, Mosaic, Neighbor-preserving & US, China & 34 - 49 & \citeyear{sun2010Effectiveness} \\
			\hline
			\citet{cruz2017Adapted} & \citep{cruz2017Adapted} & Dorling, Non-contiguous, Neighbor-preserving & Portugal & 2,882 & \citeyear{cruz2017Adapted} \\
			\hline
			\citet{tong2018Cartograms} & \citep{tong2018Cartograms} & Demers & England & 209 & \citeyear{tong2018Cartograms} \\
			\hline
			\citet{gao2020Visualising} & \citep{gao2020Visualising} & Dorling & China & 34 & \citeyear{gao2020Visualising} \\
			\hline
			\citet{nusrat2020Recognition} & \citep{nusrat2020Recognition} & Contiguous, Dorling & Portugal & 49 & \citeyear{nusrat2020Recognition} \\
			\hline
			\citet{nickel2022Multicriteria} & \citep{nickel2022Multicriteria} & Contiguous, Demers & US, Netherlands, World & 49 - 342 & \citeyear{nickel2022Multicriteria} \\
			\hline

>>>>

{
\renewcommand{\arraystretch}{1.5}
\begin{table*}[!tb]
	\centering
	\resizebox{\textwidth}{!}{
		\begin{tabulary}{\textwidth}{|*{4}{l|}r|c|}
			\hhline{~|*{4}{-}|~}
			\multicolumn{1}{c|}{\textbf{Literature}} &
			\textbf{Cartogram Type(s)} &
			\textbf{Geographic Region(s)} &
			\textbf{Number of Nodes} &
			\multicolumn{1}{c}{\textbf{Year}} \\
			\hline

			% \citet{auber2007Geographical} & \citep{auber2007Geographical} & US & 19 & 2007 \\
			% \hline
			\citet{warf2008Geography} & Dorling & US & 3,142 & \citeyear{warf2008Geography} \\
			\hline
			\citet{sun2010Effectiveness} & Dorling, Mosaic, Neighbor-preserving & US, China & 34 - 49 & \citeyear{sun2010Effectiveness} \\
			\hline
			\citet{cruz2017Adapted} & Dorling, Non-contiguous, Neighbor-preserving & Portugal & 2,882 & \citeyear{cruz2017Adapted} \\
			\hline
			\citet{tong2018Cartograms} & Demers & England & 209 & \citeyear{tong2018Cartograms} \\
			\hline
			\citet{gao2020Visualising} & Dorling & China & 34 & \citeyear{gao2020Visualising} \\
			\hline
			\citet{nusrat2020Recognition} & Contiguous, Dorling & Portugal & 49 & \citeyear{nusrat2020Recognition} \\
			\hline
			\citet{nickel2022Multicriteria} & Contiguous, Demers & US, Netherlands, World & 49 - 342 & \citeyear{nickel2022Multicriteria} \\
			\hline
